---
title: "Annual sales analysis"
author: "Lanxin Xiang"
date: "2024-10-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS) #<---boxcox
library(stats)  #<---for cooks.distance
library(faraway) #<--halfnorm
library(caret) #<---boxcox lambda
library(lawstat) # run test
library(lmtest) # dw test, levene test
library(nortest) # ad test
library(onewaytests) #  BF Test
library(boot)
```

## Load data
```{r}
x <- seq(0,9)
y <- c(98, 135, 162, 178, 221, 232, 283, 300, 374, 395)
x_c <- x - mean(x)
data <- data.frame(x, x_c, y)
```

## Descriptive Analysis

```{r}
summary(y)
par(mfrow = c(1,2))
boxplot(y, ylab = 'Sales')
plot(x, y, xlab = 'Year', ylab = 'Sales', )
```
## Propose Models

```{r}
lmfit1 <- lm(y~x)
lmfit2 <- lm(y~0+x)
```

```{r}
bc1 <- boxcox(lmfit1, plotit=T)
```

```{r}
lambda1 <- bc1$x[which.max(bc1$y)]
```

```{r}
ybc1 <- (y^lambda1-1)/lambda1
lmbc1 <- lm(ybc1~x)
```


## Diagnostics

### lmfit1

y~b0+b1x+elsilon

```{r}
summary(lmfit1)
```

```{r}
# influential points
cook1 <- cooks.distance(lmfit1)
par(mfcol=c(1,2))
halfnorm(cook1,3,ylab="Cooks dist")
boxplot(cook1)
```


```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(lmfit1),residuals(lmfit1),xlab="Fitted Annual Sales",ylab="Residuals")
abline(h=0)
plot(fitted(lmfit1),abs(residuals(lmfit1)),xlab="Fitted Annual Sales",ylab="|Residuals|")
```

```{r}
lmfit1$residuals
```

(+++)(-----)(++)
num. of run=3
postive = 5
negative = 5

rL = 2 rU = 10
do not reject the null hypothesis

```{r}
## randomness cont.
#runs.test(residuals(lmfit1)) # large sample
dwtest(lmfit1)
```

```{r}
## constant variance BF test
set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
for (i in 1:rounds){
  group <- sample(c(rep(1,5), rep(0,5)))
  temp <- data.frame(res = residuals(lmfit1), group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(x, lmfit1$residuals^2, xlab='Year', ylab='Residuals^2')
bptest(lmfit1)

res21 <- lmfit1$residuals^2
bp1 <- lm(res21~x)
ssr1 <- sum((bp1$fitted.values-mean(res21))^2)

bpt1 <- (ssr1/2)/(sum(res21)/10)^2
bpt1
1-pchisq(bpt1, 1)
```


```{r}
## normality test
qqnorm(residuals(lmfit1), ylab="Residuals")
qqline(residuals(lmfit1))

shapiro.test(residuals(lmfit1))
ad.test(residuals(lmfit1))
```

### lmfit2

y~b1x+elsilon

```{r}
# influential points
cook2 <- cooks.distance(lmfit2)
par(mfcol=c(1,2))
halfnorm(cook2,3,ylab="Cooks dist")
boxplot(cook2)
```


```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(lmfit2),residuals(lmfit2),xlab="Fitted Annual Sales",ylab="Residuals")
abline(h=0)
plot(fitted(lmfit2),abs(residuals(lmfit2)),xlab="Fitted Annual Sales",ylab="|Residuals|")
```

```{r}
lmfit2$residuals
```

(+++++)(-)(+)(---)
num. of run=4
postive = 6
negative = 4

rL = 2 rU = 9
do not reject the null hypothesis

```{r}
## randomness cont.
#runs.test(residuals(lmfit1)) # large sample
dwtest(lmfit2)
```
Not random!!

```{r}
## constant variance BF test
set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
for (i in 1:rounds){
  group <- sample(c(rep(1,5), rep(0,5)))
  temp <- data.frame(res = residuals(lmfit2), group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(x, lmfit2$residuals^2, xlab='Year', ylab='Residuals^2')
bptest(lmfit2, varformula = ~1+x)
```


```{r}
res22 <- lmfit2$residuals^2
bp2 <- lm(res22~x)
ssr2 <- sum((bp2$fitted.values-mean(res22))^2)

bpt2 <- (ssr2/2)/(sum(res22)/10)^2
bpt2
1-pchisq(bpt2, 1)
```
reject 


```{r}
## normality test
qqnorm(residuals(lmfit2), ylab="Residuals")
qqline(residuals(lmfit2))

shapiro.test(residuals(lmfit2))
ad.test(residuals(lmfit2))
```


### lmbc1

boxcox(y)~b0+b1x+elsilon

```{r}
# influential points
cook4 <- cooks.distance(lmbc1)
par(mfcol=c(1,2))
halfnorm(cook4,3,ylab="Cooks dist")
boxplot(cook4)
```


```{r}
plot(x, ybc1, xlab='Year', ylab='BoxCox(Anuual Sales)')
```

```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(lmbc1),residuals(lmbc1),xlab="Fitted Annual Sales",ylab="Residuals")
abline(h=0)
plot(fitted(lmbc1),abs(residuals(lmbc1)),xlab="Fitted Annual Sales",ylab="|Residuals|")
```

```{r}
lmbc1$residuals
```

(-)(++)(-)(+)(-)(+)(-)(+)(-)

num. of run=9
postive = 5
negative = 5

rL = 2 rU = 10
do not reject the null hypothesis

```{r}
## randomness cont.
#runs.test(residuals(lmfit1)) # large sample
dwtest(lmbc1)
```

```{r}
## constant variance BF test
set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- residuals(lmbc1)
for (i in 1:rounds){
  group <- sample(c(rep(1,5), rep(0,5)))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(x, lmbc1$residuals^2,  xlab='Year', ylab='Residuals^2')
bptest(lmbc1)
```

```{r}
res24 <- lmbc1$residuals^2
bp4 <- lm(res24~x)
ssr4 <- sum((bp4$fitted.values-mean(res24))^2)

bpt4 <- (ssr4/2)/(sum(res24)/10)^2
bpt4
1-pchisq(bpt4, 1)
```


```{r}
## normality test
qqnorm(residuals(lmbc1), ylab="Residuals")
qqline(residuals(lmbc1))

shapiro.test(residuals(lmbc1))
ad.test(residuals(lmbc1))
```

### wls1

```{r}
res1<-residuals(lmfit1)
absres1<-abs(res1)

lmfitw1 <- lm(absres1~x)
summary(lmfitw1)
#weight is proportion to inverse of variance
w1 <- 1/(fitted(lmfitw1))^2
wlm1 <-lm(y ~ x, weights=w1)
summary(wlm1)
```

```{r}
# influential points
cookw1 <- cooks.distance(wlm1)
par(mfcol=c(1,2))
halfnorm(cookw1,3,ylab="Cooks dist")
boxplot(cookw1)
```


```{r}
## randomness
par(mfcol=c(1,2))
w.normed <- w1/sum(w1)
weighted_res <- sqrt(w.normed)*residuals(wlm1)
plot(fitted(wlm1),weighted_res,xlab="Fitted Annual Sales",ylab="Weighted Residuals")
abline(h=0)
plot(fitted(wlm1),abs(weighted_res),xlab="Fitted Annual Sales",ylab="|Weighted Residuals|")
```

```{r}
weighted_res
```

(+++)(-----)(++)
num. of run=3
postive = 5
negative = 5

rL = 2 rU = 10
do not reject the null hypothesis

```{r}
## randomness cont.
#runs.test(residuals(lmfit1)) # large sample
dwtest(wlm1)
```

```{r}
## constant variance BF test
set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- weighted_res
for (i in 1:rounds){
  group <- sample(c(rep(1,5), rep(0,5)))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(x, weighted_res^2, xlab='Year', ylab='(Weighted Residuals)^2')
bptest(wlm1)
```

```{r}
resw21 <- weighted_res^2
bpw1 <- lm(resw21~x, weights = w1)
ssrw1 <- sum((bpw1$fitted.values-mean(resw21))^2)

bptw1 <- (ssrw1/2)/(sum(resw21)/10)^2

bptw1
1-pchisq(bptw1, 1)
```


```{r}
## normality test
qqnorm(weighted_res, ylab="Weighted Residuals")
qqline(weighted_res)

shapiro.test(weighted_res)
ad.test(weighted_res)
```


### Model selection
```{r}
loocv_lm <- function(data, expression = expr(y~x), K = 10) {
  errors <- numeric(K)
  folds <- seq(1:K)
  for (k in 1:K) {
    train_data <- data[folds != k, ]
    test_data <- data[folds == k, ]
    
    fit <- lm(expression, data = train_data)
    predictions <- predict(fit, newdata = test_data)
    errors[k] <- (test_data$y - predictions)^2
  }
  return(errors)
}

loocv_lmbc <- function(data, y.og, lambda, expression = expr(y~x), K = 10) {
  errors <- numeric(K)
  folds <- seq(1:K)
  for (k in 1:K) {
    train_data <- data[folds != k, ]
    test_data <- data[folds == k, ]
    
    fit <- lm(expression, data = train_data)
    predictions <- predict(fit, newdata = test_data)
    e.yhat <- (lambda*predictions + 1)^(1/lambda)
    errors[k] <- (y.og[k] - e.yhat)^2
  }
  return(errors)
}

weighted_loocv_glm <- function(data, expression = expr(y~x), K = 10) {
  errors <- numeric(K)
  folds <- seq(1:K)
  for (k in 1:K) {
    train_data <- data[folds != k, ]
    test_data <- data[folds == k, ]
    fit <- lm(expression, data = train_data, weights = train_data$w)
    predictions <- predict(fit, newdata = test_data)
    errors[k] <- (test_data$y - predictions)^2*test_data$w
  }
  
  return(errors)
}
```


```{r}
cv1 <- loocv_lm(data=data.frame(x=x, y=y), expression = expr(y~x), K = 10)

cvbc1 <- loocv_lmbc(data=data.frame(x=x, y=ybc1), y.og=y,lambda = lambda1, expression = expr(y~x), K = 10)

gwlm1 <- weighted_loocv_glm(data=data.frame(x=x, y=y, w=w.normed), expression = expr(y~x), K = 10)

boxplot((data.frame("SLR" = cv1, "SLR w Box-Cox"=cvbc1, "SLR w WLS"=gwlm1*10)))
```

### Inference
```{r}
summary(lmfit1)
confint(lmfit1)
```

```{r}
predict(lmfit1, newdata = data.frame(x=10))
predict(lmfit1, newdata = data.frame(x=10), interval='confidence')
predict(lmfit1, newdata = data.frame(x=10), interval='prediction')
```
