---
title: "Annual sales analysis"
author: "Lanxin Xiang"
date: "2024-11-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS) #<---boxcox
library(stats)  #<---for cooks.distance
library(faraway) #<--halfnorm
library(caret) #<---boxcox lambda
library(lawstat) # run test
library(lmtest) # dw test, levene test
library(nortest) # ad test
library(onewaytests) #  BF Test
library(boot)
```

## Load data
```{r}
data <- read.table("24tpdataFall24_n189.txt", header = TRUE)
n <- length(data$Biomarker)
str(data)
```

## Descriptive Analysis

```{r}
summary(data$Biomarker)
par(mfrow = c(1,2))
boxplot(data$Biomarker, ylab = 'Biomarker')
plot(data$GeneExpression, data$Biomarker, xlab = 'Gene Expression', ylab = 'Biomarker' )
```
## Propose Models and Diagnostics

### lmfit

y~b0+b1x+elsilon

```{r}
lmfit <- lm(Biomarker~GeneExpression, data = data)
summary(lmfit)
```

```{r}
# influential points
lm.cooks <- cooks.distance(lmfit)
par(mfcol=c(1,2))
halfnorm(lm.cooks,3,ylab="Cooks dist")
boxplot(lm.cooks)
```


```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(lmfit),residuals(lmfit),xlab="Fitted Biomarker",ylab="Residuals")
abline(h=0)
plot(fitted(lmfit),abs(residuals(lmfit)),xlab="Fitted Biomarker",ylab="|Residuals|")
```

```{r}
## randomness cont.
runs.test(residuals(lmfit)) # large sample
# dwtest(lmfit_cl) no time dependence
```

```{r}
## constant variance BF test

set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- residuals(lmfit)
for (i in 1:rounds){
  group <- sample(c(rep(1,n %/% 2), rep(0,n-(n %/% 2))))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(data$GeneExpression, lmfit$residuals^2, xlab='Gene Expression', ylab='Residuals^2')
bptest(lmfit)

res2_lm <- lmfit$residuals^2
bp_lm <- lm(res2_lm~data$GeneExpression)
ssr_lm <- sum((bp_lm$fitted.values-mean(res2_lm))^2)

bpt_lm <- (ssr_lm/2)/(sum(res2_lm)/n)^2
bpt_lm
1-pchisq(bpt_lm, 1)
```
reject BP test !!

```{r}
## normality test
qqnorm(residuals(lmfit), ylab="Residuals")
qqline(residuals(lmfit))

shapiro.test(residuals(lmfit))
ks.test(residuals(lmfit), "pnorm", mean = mean(residuals(lmfit)), sd = sd(residuals(lmfit)))
```
### lmbc

boxcox(y)~b0+b1x+elsilon

y >0 no need to shift
```{r}
min(data$Biomarker)
```

```{r}
bc <- boxcox(lmfit, plotit=T)
```

```{r}
lambda <- bc$x[which.max(bc$y)]
lambda
```

```{r}
marker.bc <- (data$Biomarker^lambda-1)/lambda
plot(data$GeneExpression, marker.bc, xlab = 'Gene Expression', ylab = 'BoxCox(Biomarker)')
```
```{r}
lmbc <- lm(marker.bc~data$GeneExpression)
summary(lmbc)
```

```{r}
# influential points
bc.cooks <- cooks.distance(lmbc)
par(mfcol=c(1,2))
halfnorm(bc.cooks,3,ylab="Cooks dist")
boxplot(bc.cooks)
```


```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(lmbc),residuals(lmbc),xlab="Fitted Biomarker",ylab="Residuals")
abline(h=0)
plot(fitted(lmbc),abs(residuals(lmbc)),xlab="Fitted Biomarker",ylab="|Residuals|")
```


```{r}
## randomness cont.
runs.test(residuals(lmbc)) # large sample
# dwtest(lmbc)
```

```{r}
## constant variance BF test

set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- residuals(lmbc)
for (i in 1:rounds){
  group <- sample(c(rep(1,n %/% 2), rep(0,n-(n %/% 2))))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

```{r}
plot(data$Biomarker, lmbc$residuals^2,  xlab='Gene Expression', ylab='Residuals^2')
bptest(lmbc)
```


```{r}
res2_bc <- lmbc$residuals^2
bp_bc <- lm(res2_bc~data$GeneExpression + I(data$GeneExpression^2))
ssr_bc <- sum((bp_bc$fitted.values-mean(res2_bc))^2)

bpt_bc <- (ssr_bc/2)/(sum(res2_bc)/n)^2
bpt_bc
1-pchisq(bpt_bc, 2)
```

reject

```{r}
## normality test
qqnorm(residuals(lmbc), ylab="Residuals")
qqline(residuals(lmbc))

shapiro.test(residuals(lmbc))
ks.test(residuals(lmbc), "pnorm", mean = mean(residuals(lmbc)), sd = sd(residuals(lmbc)))
ad.test(residuals(lmbc))
```

### wls

```{r}
lmres <- residuals(lmfit)
abslmres<-abs(lmres)
plot(data$GeneExpression, abslmres, xlab='Gene Expression', ylab='|Residuals|')
```

```{r}
lmw <- lm(abslmres~data$GeneExpression + I(data$GeneExpression^2))
summary(lmw)
```

```{r}
#weight is proportion to inverse of variance
w <- 1/(fitted(lmw))^2
wlm <- lm(Biomarker~GeneExpression, data = data, weights = w)
summary(wlm)
```

```{r}
# influential points
cookw <- cooks.distance(wlm)
par(mfcol=c(1,2))
halfnorm(cookw,3,ylab="Cooks dist")
boxplot(cookw)
```


```{r}
## randomness
par(mfcol=c(1,2))
w.normed <- w/sum(w)
weighted_res <- sqrt(w.normed)*residuals(wlm)
plot(fitted(wlm),weighted_res,xlab="Fitted Biomarker",ylab="Weighted Residuals")
abline(h=0)
plot(fitted(wlm),abs(weighted_res),xlab="Fitted Biomarker",ylab="|Weighted Residuals|")
```


```{r}
## randomness cont.
runs.test(weighted_res) # large sample
# dwtest(wlm)
```

```{r}
## constant variance BF test

set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- weighted_res
for (i in 1:rounds){
  group <- sample(c(rep(1,n %/% 2), rep(0,n-(n %/% 2))))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(data$GeneExpression, weighted_res^2, xlab='Gene Expression', ylab='(Weighted Residuals)^2')
bptest(wlm)
```

```{r}
res2_wlm <- weighted_res^2
bp_wlm <- lm(res2_wlm~data$GeneExpression)
ssr_wlm <- sum((bp_wlm$fitted.values-mean(res2_wlm))^2)

bpt_wlm <- (ssr_wlm/2)/(sum(res2_wlm)/n)^2
bpt_wlm
1-pchisq(bpt_wlm, 1)
```

reject

```{r}
## normality test
qqnorm(weighted_res, ylab="Weighted Residuals")
qqline(weighted_res)

shapiro.test(weighted_res)
ad.test(weighted_res)
```
not normal but we can use bootstrapping to estimate

### 1/y link

1/y~b0+b1x+elsilon

```{r}
bio.new <- 1/data$Biomarker
plot(data$GeneExpression, bio.new, xlab = 'Gene Expression', ylab = '1/Biomarker' )
```

```{r}
linklm <- lm(bio.new~data$GeneExpression)
summary(linklm)
```

```{r}
# influential points
linklm.cooks <- cooks.distance(linklm)
par(mfcol=c(1,2))
halfnorm(linklm.cooks,3,ylab="Cooks dist")
boxplot(linklm.cooks)
```


```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(linklm),residuals(linklm),xlab="Fitted Biomarker",ylab="Residuals")
abline(h=0)
plot(fitted(linklm),abs(residuals(linklm)),xlab="Fitted Biomarker",ylab="|Residuals|")
```

```{r}
## randomness cont.
runs.test(residuals(linklm)) # large sample
# dwtest(lmfit_cl) no time dependence
```

```{r}
## constant variance BF test

set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- residuals(linklm)
for (i in 1:rounds){
  group <- sample(c(rep(1,n %/% 2), rep(0,n-(n %/% 2))))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(data$GeneExpression, linklm$residuals^2, xlab='Gene Expression', ylab='Residuals^2')
bptest(linklm)

res2_linklm <- linklm$residuals^2
bp_linklm <- lm(res2_linklm~data$GeneExpression)
ssr_linklm <- sum((bp_linklm$fitted.values-mean(res2_linklm))^2)

bpt_linklm <- (ssr_linklm/2)/(sum(res2_linklm)/n)^2
bpt_linklm
1-pchisq(bpt_linklm, 1)
```
not reject BP test !!

```{r}
## normality test
qqnorm(residuals(linklm), ylab="Residuals")
qqline(residuals(linklm))

shapiro.test(residuals(linklm))
ks.test(residuals(linklm), "pnorm", mean = mean(residuals(linklm)), sd = sd(residuals(linklm)))
```

### Quadratic 

y = b0+b1x+b2x^2

```{r}
qlm <- lm(Biomarker~GeneExpression + I(GeneExpression^2), data = data)
summary(qlm)
```

```{r}
test_x <- data$GeneExpression+2000
qlm_test <- lm(data$Biomarker~test_x + I(test_x^2))
summary(qlm_test)
```
```{r}
# influential points
qlm.cooks <- cooks.distance(qlm)
par(mfcol=c(1,2))
halfnorm(qlm.cooks,3,ylab="Cooks dist")
boxplot(qlm.cooks)
```




```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(qlm),residuals(qlm),xlab="Fitted Biomarker",ylab="Residuals")
abline(h=0)
plot(fitted(qlm),abs(residuals(qlm)),xlab="Fitted Biomarker",ylab="|Residuals|")
```

```{r}
## randomness cont.
runs.test(residuals(qlm)) # large sample
# dwtest(lmfit_cl) no time dependence
```

```{r}
## constant variance BF test

set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- residuals(qlm)
for (i in 1:rounds){
  group <- sample(c(rep(1,n %/% 2), rep(0,n-(n %/% 2))))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(data$GeneExpression, qlm$residuals^2, xlab='Gene Expression', ylab='Residuals^2')
bptest(qlm)

res2_qlm <- qlm$residuals^2
bp_qlm <- lm(res2_qlm~data$GeneExpression)
ssr_qlm <- sum((bp_qlm$fitted.values-mean(res2_qlm))^2)

bpt_qlm <- (ssr_qlm/2)/(sum(res2_qlm)/n)^2
bpt_qlm
1-pchisq(bpt_qlm, 2)
```
reject BP test ?

```{r}
## normality test
qqnorm(residuals(qlm), ylab="Residuals")
qqline(residuals(qlm))

shapiro.test(residuals(qlm))
ks.test(residuals(qlm), "pnorm", mean = mean(residuals(qlm)), sd = sd(residuals(qlm)))
```
### qlmbc

boxcox(y)~b0+b1x+b2x^2+elsilon

y > 0 no need to shift
```{r}
min(data$Biomarker)
```

```{r}
bc2 <- boxcox(qlm, plotit=T)
```

```{r}
lambda2 <- bc2$x[which.max(bc2$y)]
lambda2
```


```{r}
marker.bc2 <- (data$Biomarker^lambda2-1)/lambda2
plot(data$GeneExpression, marker.bc2, xlab = 'Gene Expression', ylab = 'BoxCox(Biomarker)')
```
```{r}
qlmbc <- lm(marker.bc2~data$GeneExpression + I(data$GeneExpression^2))
summary(qlmbc)

testqlm <- lm(marker.bc2~test_x + I(test_x^2))
summary(testqlm)
```

```{r}
# influential points
qcook_bc <- cooks.distance(qlmbc)
par(mfcol=c(1,2))
halfnorm(qcook_bc,3,ylab="Cooks dist")
boxplot(qcook_bc)
```


```{r}
## randomness
par(mfcol=c(1,2))
plot(fitted(qlmbc),residuals(qlmbc),xlab="Fitted Biomarker",ylab="Residuals")
abline(h=0)
plot(fitted(qlmbc),abs(residuals(qlmbc)),xlab="Fitted Biomarker",ylab="|Residuals|")
```


```{r}
## randomness cont.
runs.test(residuals(qlmbc)) # large sample
# dwtest(lmbc)
```

```{r}
## constant variance BF test

set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- residuals(qlmbc)
for (i in 1:rounds){
  group <- sample(c(rep(1,n %/% 2), rep(0,n-(n %/% 2))))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

```{r}
plot(data$Biomarker, qlmbc$residuals^2,  xlab='Gene Expression', ylab='Residuals^2')
bptest(qlmbc)
```


```{r}
res2_qbc <- qlmbc$residuals^2
bp_qbc <- lm(res2_qbc~data$GeneExpression + I(data$GeneExpression^2))
ssr_qbc <- sum((bp_qbc$fitted.values-mean(res2_qbc))^2)

bpt_qbc <- (ssr_qbc/2)/(sum(res2_qbc)/n)^2
bpt_qbc
1-pchisq(bpt_qbc, 2)
```

reject

```{r}
## normality test
qqnorm(residuals(qlmbc), ylab="Residuals")
qqline(residuals(qlmbc))

shapiro.test(residuals(qlmbc))
ad.test(residuals(qlmbc))
```

### qwls

```{r}
qlmres <- residuals(qlm)
absqlmres <-abs(qlmres)
plot(data$GeneExpression, absqlmres, xlab='Gene Expression', ylab='|Residuals|')
```

```{r}
qlmw <- lm(absqlmres~data$GeneExpression + I(data$GeneExpression^2))
summary(qlmw)
```

```{r}
#weight is proportion to inverse of variance
qw <- 1/(fitted(qlmw))^2
qwlm <- lm(Biomarker~GeneExpression + I(GeneExpression^2), data = data, weights = qw)
summary(qwlm)
```

```{r}
# influential points
qcookw <- cooks.distance(qwlm)
par(mfcol=c(1,2))
halfnorm(qcookw,3,ylab="Cooks dist")
boxplot(qcookw)
```
```{r}
## randomness
par(mfcol=c(1,2))
qw.normed <- qw/sum(qw)
qweighted_res <- sqrt(qw.normed)*residuals(qwlm)
plot(fitted(qwlm),qweighted_res,xlab="Fitted Biomarker",ylab="Weighted Residuals")
abline(h=0)
plot(fitted(qwlm),abs(qweighted_res),xlab="Fitted Biomarker",ylab="|Weighted Residuals|")
```

```{r}
## randomness cont.
runs.test(qweighted_res) # large sample
# dwtest(qwlm)
```

```{r}
## constant variance BF test

set.seed(42)
rounds <- 10000
bf_p <- rep(NA, rounds)
res <- qweighted_res
for (i in 1:rounds){
  group <- sample(c(rep(1,n %/% 2), rep(0,n-(n %/% 2))))
  temp <- data.frame(res = res, group = group)
  bf <- bf.test(res~factor(group), data = temp, verbose = FALSE)
  bf_p[i] <- bf$p.value
}
sum(bf_p>0.05)/rounds
```

do not reject the null hypothesis BF test

```{r}
plot(data$GeneExpression, qweighted_res^2, xlab='Gene Expression', ylab='(Weighted Residuals)^2')
bptest(qwlm)
```

```{r}
res2_qwlm <- qweighted_res^2
bp_qwlm <- lm(res2_qwlm~data$GeneExpression)
ssr_qwlm <- sum((bp_qwlm$fitted.values-mean(res2_qwlm))^2)

bpt_qwlm <- (ssr_qwlm/2)/(sum(res2_qwlm)/n)^2
bpt_qwlm
1-pchisq(bpt_qwlm, 2)
```

not reject

```{r}
## normality test
qqnorm(qweighted_res, ylab="Weighted Residuals")
qqline(qweighted_res)

shapiro.test(qweighted_res)
ks.test(qweighted_res, "pnorm", mean = mean(qweighted_res), sd = sd(qweighted_res))

```
not normal but we can use bootstrapping to estimate


## Model selection


```{r}
expression <- expr(Biomarker~GeneExpression + I(GeneExpression^2))
```


```{r}
getPredictionError <- function(train, test, expression){
  fit <- lm(expression, data = train)
  predictions <- predict(fit, newdata = test)
  errors <- (test$Biomarker - predictions)^2
  MSE <- mean(errors)
  return (list(errors, MSE))
}

getWeightedPredictionError <- function(train, test, expression){
  lmfit <- lm(expression, data=train)
  absres <- abs(residuals(lmfit) - train$Biomarker)
  wfit <- lm(absres~train$GeneExpression+I(train$GeneExpression^2))
  train_w <- 1/(fitted(wfit))^2
  train$w <- train_w/sum(train_w)
  
  fit <- lm(expression, data = train, weights = train$w)
  
  test_w <- rep(NA, length(test$Biomarker))
  for (i in 1: length(test$Biomarker)){
    test_w[i] <- 1/(wfit$coefficients[1]+wfit$coefficients[2]*test$Biomarker[i]+wfit$coefficients[3]*test$Biomarker[i]^2)^2
  }
  
  test$w <- test_w/sum(test_w)
  predictions <- predict(fit, newdata = test)
  errors <- (test$Biomarker - predictions)^2
  MSE <- sum(errors*test$w)
  return (list(errors, MSE))
}

getPredictionErrorLink <- function(train, test){
  y.new <- 1/train$Biomarker
  train.new <- data.frame(y=y.new, GeneExpression=train$GeneExpression)
  fit <- lm(y~GeneExpression, data=train.new)
  predictions <- predict(fit, newdata = test)
  errors <- (test$Biomarker - 1/predictions)^2
  MSE <- mean(errors)
  return (list(errors, MSE))
}
```



```{r}
set.seed(42)

train_idx <- sample(1:n, floor(n*0.7))
test_idx <- setdiff(c(1:n), train_idx)
train <- data[train_idx, ]
test <- data[test_idx, ]
```

```{r}
ls_error <- getPredictionError(train, test, expr(Biomarker~GeneExpression))

wls_error <- getWeightedPredictionError(train, test, expr(Biomarker~GeneExpression))
qlm_error <- getPredictionError(train, test, expr(Biomarker~GeneExpression + I(GeneExpression^2)))
qwls_error <- getWeightedPredictionError(train, test, expr(Biomarker~GeneExpression + I(GeneExpression^2)))

linkls_error <- getPredictionErrorLink(train, test)
```

```{r}
tn <- length(test$Biomarker)
error.df <- data.frame("SLR"=ls_error[[1]],"SLR w WLS" = wls_error[[1]], "QLR"=qlm_error[[1]], "QLR w WLS"=qwls_error[[1]], "SLR w Link" = linkls_error[[1]])
boxplot(error.df)
```

```{r}
ls_error[[2]]
wls_error[[2]]
qlm_error[[2]]
qwls_error[[2]]
linkls_error[[2]]
```



## Inference

```{r}
summary(qwlm)
summary(qlm)
```
### define functions

```{r}
findGeneExpression <- function(coef0, coef1, coef2, y){
  discriminant <- coef1^2 - 4 * coef2 * (coef0 - y)
  
  if (discriminant < 0) {
    return("No real solutions for x")
  } 
  else {
    x1 <- (-coef1 + sqrt(discriminant)) / (2 * coef2)
    # x2 <- (-coef1 - sqrt(discriminant)) / (2 * coef2)
  }
  return (x1)
}
```

```{r}
inference1 <- function (data, expression, newx, newy){
  lmfit <- lm(expression, data=data)
  absres <- abs(residuals(lmfit) - data$Biomarker)
  wfit <- lm(absres~data$GeneExpression+I(data$GeneExpression^2))
  w <- 1/(fitted(wfit))^2
  data$w <- w
  
  fit <- lm(expression, data = data, weights = data$w)
  b1 <- fit$coefficients[2]
  b2 <- fit$coefficients[3]
  sigma <- summary(fit)$sigma
    
  pred_w <- 1/(wfit$coefficients[1]+wfit$coefficients[2]*newx+wfit$coefficients[3]*newx^2)^2
  pred_df <- data.frame(GeneExpression=newx, w=pred_w) 
  pred_new_mean <- predict(fit, pred_df)
  
  pred_new_y <- pred_new_mean + rnorm(1, 0, 1/sqrt(pred_w)*sigma)
  
  ge <- findGeneExpression(wfit$coefficients[1], wfit$coefficients[2], wfit$coefficients[3], newy)
  
  return(list(b1, b2, pred_new_mean, pred_new_y, ge))
}
```

```{r}
inference2 <- function (data, expression, newx, newy){
  lmfit <- lm(expression, data=data)
  b1 <- lmfit$coefficients[2]
  b2 <- lmfit$coefficients[3]
  sigma <- summary(lmfit)$sigma
    
  pred_new_mean <- predict(lmfit, list(GeneExpression=newx))
  pred_new_y <- pred_new_mean + rnorm(1, 0, sigma)
  
  ge <- findGeneExpression(lmfit$coefficients[1], lmfit$coefficients[2], lmfit$coefficients[3], newy)
  
  return(list(b1, b2, pred_new_mean, pred_new_y, ge))
}
```

```{r}
# bootstrapping for inference
bootstrapping <- function(data, n, B, expression, newx, newy, func){
  res <- data.frame(b1 = rep(NA, B), b2 = rep(NA, B), pred_mean = rep(NA, B), pred_val = rep(NA, B), findge=rep(NA, B))
  i <- 1
  while (i <= B) {
    index <- sample(seq(1, n), n, replace = TRUE)
    temp_data <- data[index, ]
    inference_res <- func(temp_data, expression, newx, newy)
    res[i, 'b1'] <- inference_res[[1]]
    res[i, 'b2'] <- inference_res[[2]]
    res[i, 'pred_mean'] <- inference_res[[3]]
    res[i, 'pred_val'] <- inference_res[[4]]
    res[i, 'findge'] <- inference_res[[5]]
    i <- i+1
    }
  return (res)
}
```


### find CI, PI

```{r}
set.seed(42)
res <- bootstrapping(data=data, n=n, B=10000, expression=expr(Biomarker~GeneExpression + I(GeneExpression^2)), newx=100, newy = 10, func=inference1)
```

```{r}
quantile(res$b1, probs = c(0.025, 0.975))
quantile(res$b2, probs = c(0.025, 0.975))
quantile(res$pred_mean, probs = c(0.025, 0.975))
quantile(res$pred_val, probs = c(0.025, 0.975))
quantile(res$findge, probs = c(0.025, 0.975))
```

```{r}
pred_y1 <- predict(qwlm, newdata = list(GeneExpression=100))
pred_x1 <- findGeneExpression(qwlm$coefficients[1], qwlm$coefficients[2], qwlm$coefficients[3], 10)
pred_y1
pred_x1
```

```{r}
hist(res$b1, xlab='b1', main='Bootstrapping distribution for QLR w WLS b1')
abline(v= quantile(res$b1, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= qwlm$coefficients[2], col='red')
```

```{r}
hist(res$b2, xlab='b2', main='Bootstrapping distribution for QLR w WLS b2')
abline(v= quantile(res$b2, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= qwlm$coefficients[3], col='red')
```
```{r}
hist(res$pred_mean, xlab='E(B|GE=100)', main='Bootstrapping distribution for E(B|GE=100) estimated by QLR w WLS')
abline(v= quantile(res$pred_mean, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= pred_y1, col='red')
```

```{r}
hist(res$pred_val, xlab='B|GE=100', main='Bootstrapping distribution for B|GE=100 estimated by QLR w WLS')
abline(v= quantile(res$pred_val, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= pred_y1, col='red')
```
```{r}
hist(res$findge, xlab='E(GE|B=10)', main='Bootstrapping distribution for E(GE|B=10) estimated by QLR w WLS')
abline(v= quantile(res$findge, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= pred_x1, col='red')
```

```{r}
set.seed(42)
res2 <- bootstrapping(data=data, n=n, B=10000, expression=expr(Biomarker~GeneExpression + I(GeneExpression^2)), newx=100, newy = 10, func=inference2)
```

```{r}
quantile(res2$b1, probs = c(0.025, 0.975))
quantile(res2$b2, probs = c(0.025, 0.975))
quantile(res2$pred_mean, probs = c(0.025, 0.975))
quantile(res2$pred_val, probs = c(0.025, 0.975))
quantile(res2$findge, probs = c(0.025, 0.975))
```

```{r}
pred_y2 <- predict(qlm, newdata = list(GeneExpression=100))
pred_x2 <- findGeneExpression(qlm$coefficients[1], qlm$coefficients[2], qlm$coefficients[3], 10)
pred_y2
pred_x2
```

```{r}
hist(res2$b1, xlab='b1', main='Bootstrapping distribution for QLR b1')
abline(v= quantile(res2$b1, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= qlm$coefficients[2], col='red')
```

```{r}
hist(res2$b2, xlab='b2', main='Bootstrapping distribution for QLR b2')
abline(v= quantile(res2$b2, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= qlm$coefficients[3], col='red')
```

```{r}
hist(res2$pred_mean, xlab='E(B|GE=100)', main='Bootstrapping distribution for E(B|GE=100) estimated by QLR')
abline(v= quantile(res2$pred_mean, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= pred_y2, col='red')
```

```{r}
hist(res2$pred_val, xlab='B|GE=100', main='Bootstrapping distribution for B|GE=100 estimated by QLR')
abline(v= quantile(res2$pred_val, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= pred_y2, col='red')
```

```{r}
hist(res2$findge, xlab='E(GE|B=10)', main='Bootstrapping distribution for E(GE|B=10) estimated by QLR')
abline(v= quantile(res2$findge, probs = c(0.025, 0.975)), col='blue', lty = 2)
abline(v= pred_x2, col='red')
```